\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Numeric Methods Benchmark Analysis}

\author{\IEEEauthorblockN{1\textsuperscript{st} Santiago Valencia Arango}
\IEEEauthorblockA{\textit{dept. of science} \\
\textit{EAFIT}\\
Medellín, Colombia \\
svalenciaa@eafit.edu.co}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Juan Manuel Young Hoyos}
\IEEEauthorblockA{\textit{dept. of science} \\
\textit{EAFIT (of Aff.)}\\
Medellín, Colombia \\
jmyoungh@eafit.edu.co}
}

\maketitle

\begin{abstract}
The idea of this project is to test out if it is worth it to use C++ instead of Python for
algorithms of some numeric methods, like finding roots of non-linear equations using
Newton-Raphson's method.
\end{abstract}

\begin{IEEEkeywords}
Numeric methods, C++, Python, algorithms, insert
\end{IEEEkeywords}

\section{Introduction}
Why this project? the aim of this project is to be able to analyze and draw a conclusion to 
the question, is it worth spending more time programming in C ++? Or is it more profitable to do 
this type of algorithms using Python and its libraries in terms of development time and program performance?

\section{What will we test?}

\subsection{Algorithms}
In this project we will only find roots of an equation using:
\begin{itemize}
    \item Newton-Rapshon method.
    \item Bisection method.
    \item Secant method.
    \item Regula-Falsi method.
    \item Fixed-point iteration method.
\end{itemize}

\subsection{G++ compiler}
\textit{g++ (Ubuntu 9.3.0-17ubuntu1~20.04) 9.3.0}

\subsection{Python interpreter}
\textit{Python 3.8.5}

\section{Newton-Raphson comparison}
\subsection{Variables}

Equation: \(x^3 + x^2 + 3\) 

Initial point: \(-20\)

Tolerance: \(0.00001\) 

Maximum number of iterations: \(20\)

 

\begin{thebibliography}{00}
\bibitem{b1} Burden, Richard L. and Faires, Duglas. Análisis Numérico. Editorial Thomson. 9 Edición 2011.
\end{thebibliography}

\end{document}
